Abstract Spatial Specification of Stencil Computations

### 2016-06-23 paper.tex
First use of abbreviation is expanded

\begin{abstract}
  Verifying the correctness of numerical computations is hard because
  potential specifications for their behaviour tend to be highly
  decouple from the code, defined in terms of the originating
  mathematical model. For example, a system of PDEs specifies a
  relationship between variables, but tools for encoding such a
  specification, and pertinent properties such as convergence and
  stability, are rare.  Furthermore, checking the correctness of some
  implementation of a discrete approximation against such
  specifications is extremely challenging. We seek intermediate
  systems of specification and verification between lower-level
  aspects (\eg{}, out-of-bounds errors) and full correctness
  with-respect to a numerical model. In this paper, we focus on
  \emph{stencil computations}-- a common idiom in numerical code, but
  one which is prone to error due to fine-grained programming
  mistakes.  Our conjecture is that the vast majority of stencil
  computations have a simple, regular, static shape that can be
  described by a simple specification language. We propose a language
  for this, along with an inference and checking procedure. We test
  our conjecture against a corpus of numerical Fortran code, and show
  that static specifications can be given to $X\%$ of identifiable
  stencil computations, with a mean ratio of $Y:Z$
  specification-to-program code. This paper details our stencil
  specification language, its static semantics, inference, checking,
  and program synthesis procedures, our implementation, and our
  evaluation study.
\end{abstract}

>>>>

\begin{abstract}
  Verifying the correctness of numerical computations is hard because
  potential specifications for their behaviour tend to be highly
  decouple from the code, defined in terms of the originating
  mathematical model. For example, a system of partial differential equations
  (PDEs) specifies a relationship between variables, but tools for encoding such
  a specification, and pertinent properties such as convergence and
  stability, are rare.  Furthermore, checking the correctness of some
  implementation of a discrete approximation against such
  specifications is extremely challenging. We seek intermediate
  systems of specification and verification between lower-level
  aspects (\eg{}, out-of-bounds errors) and full correctness
  with-respect to a numerical model. In this paper, we focus on
  \emph{stencil computations}-- a common idiom in numerical code, but
  one which is prone to error due to fine-grained programming
  mistakes.  Our conjecture is that the vast majority of stencil
  computations have a simple, regular, static shape that can be
  described by a simple specification language. We propose a language
  for this, along with an inference and checking procedure. We test
  our conjecture against a corpus of numerical Fortran code, and show
  that static specifications can be given to $X\%$ of identifiable
  stencil computations, with a mean ratio of $Y:Z$
  specification-to-program code. This paper details our stencil
  specification language, its static semantics, inference, checking,
  and program synthesis procedures, our implementation, and our
  evaluation study.
\end{abstract}
